Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-08 src/article.tex
Revise implementation section

Scaffolder is written in the Ruby programming language, version 1.8.7
\cite{ruby-lang}. The scaffolder package is split into two libraries. The first
called ``scaffolder'' contains the core Scaffolder application programming
interface (API). The second library ``scaffolder-tools'' contains the
Scaffolder command line interface (CLI). \pb

@@

Initial sequencing data assembly may result in an incomplete genome build.
Generation of additional sequences either through PCR or computational methods
means that genome scaffolding may be an on-going process. The scaffold file
should therefore be simple to update manually in addition to being
computationally tractable. This requirement was also best suited to YAML which
is human-readable and simple to edit in a standard text editor. \pb

The scaffold file takes the form of a list of entries. Each entry corresponds
to a region of sequence used in the final scaffold sequence. The Scaffolder
software processes this list in order, converting each entry to the
corresponding nucleotide sequence, all entries are then concatenated to produce
a draft super sequence. Each entry in the scaffold file may have attributes
that define whether a sub-sequence or the reverse complement of the sequence
should be used. The types of attributes available, and an example scaffold file
are outlined below. \pb

@@

The input data for Scaffolder is nucleotide sequence in FASTA format file.
These nucleotide sequences can be of any length and for example may be
individual sequences, assembled contigs or contigs which have been joined to
into larger scaffolds. The case in which Scaffolder may be most useful is using
the contigs and scaffolded contigs produced from assembling a set of sequencing
reads. \pb

The scaffolder algorithm reads through the scaffolder file parsing each entry
in the file. Each entry is converted to corresponding sequence by fetching from
the FASTA file and then performing any designated sequence processing
operations. Each of the sequence entries are then joined as a s single super
sequence and returned to the console output. \pb

>>>>

Scaffolder is written in the Ruby programming language using version 1.8.7
\cite{ruby-lang}. The scaffolder package is split into two libraries. The
first called ``scaffolder'' provides the core Scaffolder application
programming interface (API). The second library ``scaffolder-tools'' provides
the Scaffolder command line interface (CLI). \pb

@@

Initial sequencing data assembly may result in an incomplete genome build.
Generation of additional sequences either through PCR or computational methods
means that genome scaffolding may be an on-going process. The scaffold file
should therefore be simple to update manually in addition to being
computationally tractable. This requirement was also best suited to YAML
syntax which is human-readable and simple to edit in a standard text editor.
\pb

The scaffold file takes the form of a list of entries. Each entry corresponds
to a region of sequence used in the final scaffold sequence. Each entry in the
scaffold file may have attributes that define whether a sub-sequence or the
reverse complement of the sequence should be used. The types of attributes
available, and an example scaffold file are outlined in the Results section.
\pb

@@

The input data for Scaffolder is nucleotide sequence in FASTA format file.
These nucleotide sequences can be of any length and for example may be
individual sequences, assembled contigs or contigs which have been joined to
into larger scaffolds. The case in which Scaffolder may be most useful is
using the contigs and scaffolded contigs produced from the previously
assembled set of sequencing reads, combined with additional gap filling
sequences produced by PCR or \emph{in silico} methods as outlined in the
Background. \pb

The scaffolder algorithm reads through the scaffolder file parsing. Each entry
is then converted to corresponding nucleotide sequence by fetching from the
FASTA file and then performing any designated sequence trimming or reverse
complenting. Each of the sequence entries are then joined into a continuous
single super-sequence and returned to the console output. \pb
